---
title: "BVAR TS model"
output: 
  html_document: 
    keep_md: yes
date: "2023-05-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Preprocessing

```{r libraries, echo=FALSE, message=FALSE}
#Libraries
library(tidyverse)
library(readxl)
library(xts)
library(dplyr)
library(imputeTS)
library(ggplot2)
library(MTS)
library(tseries)
library(vars)
library(bvartools)
library(xtable)

data <- read_excel("data.xlsx", sheet = 'Data')
```

```{r from char to num, echo=FALSE}
data$Pigs_heads <- as.numeric(data$Pigs_heads)
data$Head_sheep <- as.numeric(data$Head_sheep)
data$Head_goat <- as.numeric(data$Head_goat)
data$Share_of_land_under_permanent_crops <- as.numeric(data$Share_of_land_under_permanent_crops)
data$Fertilizer_used_per_area_of_cropland <- as.numeric(data$Fertilizer_used_per_area_of_cropland)
data$Share_in_land_area_Forest_Land <- as.numeric(data$Share_in_land_area_Forest_Land)
```

```{r data imputation, echo=FALSE}
data$Rail_tracks_KM <- na_interpolation(data$Rail_tracks_KM, option = 'spline')
data$Total_freight_loaded_and_unloaded <- na_interpolation(data$Total_freight_loaded_and_unloaded, option = 'spline')
data$Chicken_heads <- na_interpolation(data$Chicken_heads, option = 'spline')
data$Turkeys_heads <- na_interpolation(data$Turkeys_heads, option = 'spline')
```

```{r merge common features}
data <- data %>% 
  dplyr::mutate(livestock_heads = Pigs_heads + Head_sheep + Head_goat + 
           Chicken_heads + Turkeys_heads + Cattle_heads + Buffalo_head) 

data <- data %>% 
  dplyr::mutate(res_capacity = hydro_capacity + geothermal_capacity + 
           wind_capacity + solar_capacity + biofuels_capacity + 
           biogas_capacity + waste_capacity)

data <- data %>% dplyr::select(Year, net_greenhouse_pc, environmental_taxes, `GDP pc`,
                                 industrial_production, energy_imp_dep, naturalgas_imports,
                                 oil_imports, total_energy_supply, gross_electricity_production,
                                 res_capacity, livestock_heads,
                                 Share_of_land_under_permanent_crops, Area_harvested_Rice,
                                 Fertilizer_used_per_area_of_cropland, Share_in_land_area_Forest_Land,
                                 Rail_tracks_KM, Length_of_motorways, Number_of_motorcycle, Total_freight_loaded_and_unloaded)
```

```{r scale data}
data <- apply(data, MARGIN = 2, FUN = scale)
data <- data.frame(data)
```

```{r plot data 1/5}
par(mfrow = c(2,2))
plot(data$net_greenhouse_pc,
     type = 'l',
     xlab = "Time",
     ylab = "TON per capita - Scaled",
     main = "Net greenhouse gases emissions")

plot(data$environmental_taxes,
     type = 'l',
     xlab = "Time",
     ylab = "% of GDP - Scaled",
     main = "Environmental taxes")

plot(data$GDP.pc,
     type = 'l',
     xlab = "Time",
     ylab = "Constant 2010 US dollars - Scaled",
     main = "GDP per capita")

plot(data$industrial_production,
     type = 'l',
     xlab = "Time",
     ylab = "Index 2015=100 - Scaled",
     main = "Industrial production")

```

```{r plot data 2/5}
par(mfrow = c(2,2))
plot(data$energy_imp_dep,
     type = 'l',
     xlab = "Time",
     ylab = "% - Scaled",
     main = "Energy imports dependency")

plot(data$naturalgas_imports,
     type = 'l',
     xlab = "Time",
     ylab = "Million m^3 - Scaled",
     main = "Natural gas imports")

plot(data$oil_imports,
     type = 'l',
     xlab = "Time",
     ylab = "Thousand tonnes - Scaled",
     main = "Oil imports")

plot(data$total_energy_supply,
     type = 'l',
     xlab = "Time",
     ylab = "Gigawatt-hour - Scaled",
     main = "Total energy supply")
```

```{r plot data 3/5}
par(mfrow = c(2,2))
plot(data$gross_electricity_production,
     type = 'l',
     xlab = "Time",
     ylab = "Gigawatt-hour - Scaled - Scaled",
     main = "Gross electricity production")

plot(data$res_capacity,
     type = 'l',
     xlab = "Time",
     ylab = "Megawatt - Scaled",
     main = "Renewable Energy capacity")

plot(data$livestock_heads,
     type = 'l',
     xlab = "Time",
     ylab = "Thousand heads - Scaled",
     main = "Livestock heads")

plot(data$Share_of_land_under_permanent_crops,
     type = 'l',
     xlab = "Time",
     ylab = "% - Scaled",
     main = "Share of land under permanent crops")
```

```{r plot data 4/5}
par(mfrow = c(2,2))
plot(data$Area_harvested_Rice,
     type = 'l',
     xlab = "Time",
     ylab = "Area ha - Scaled",
     main = "Harvested rice")

plot(data$Fertilizer_used_per_area_of_cropland,
     type = 'l',
     xlab = "Time",
     ylab = "kg per ha - Scaled",
     main = "Fertilizer used per ha of cropland")

plot(data$Share_in_land_area_Forest_Land,
     type = 'l',
     xlab = "Time",
     ylab = "% - Scaled",
     main = "Share of forest land in total land")

plot(data$Rail_tracks_KM,
     type = 'l',
     xlab = "Time",
     ylab = "km - Scaled",
     main = "Rail tracks")
```

```{r plot data 5/5}
par(mfrow = c(2,2))
plot(data$Length_of_motorways,
     type = 'l',
     xlab = "Time",
     ylab = "km - Scaled",
     main = "Length of motorways")

plot(data$Number_of_motorcycle,
     type = 'l',
     xlab = "Time",
     ylab = "Units - Scaled",
     main = "Number of motorcycles")

plot(data$Total_freight_loaded_and_unloaded,
     type = 'l',
     xlab = "Time",
     ylab = "TON - Scaled",
     main = "Total aerial freight")
```

```{r first differences}
greenhouse_1 <- diff(data$net_greenhouse_pc, differences = 1)
env_tax_1 <- diff(data$environmental_taxes, differences = 1)
GDP_pc_1 <- diff(data$GDP.pc, differences = 1)
ind_prod_1 <- diff(data$industrial_production, differences = 1)
energy_imp_dep_1 <- diff(data$energy_imp_dep, differences = 1)
naturalgas_imports_1  <- diff(data$naturalgas_imports , differences = 1)
oil_imports_1  <- diff(data$oil_imports , differences = 1)
energy_supply_1 <- diff(data$total_energy_supply , differences = 1)
electricity_prod_1 <- diff(data$gross_electricity_production, differences = 1)
res_capacity_1  <- diff(data$res_capacity  , differences = 1)
livestock_heads_1 <- diff(data$livestock_heads , differences = 1)
permanent_crops_1 <- diff(data$Share_of_land_under_permanent_crops , differences = 1)
harvested_rice_1 <- diff(data$Area_harvested_Rice, differences = 1)
fertilizer_1 <- diff(data$Fertilizer_used_per_area_of_cropland, differences = 1)
forest_land_1 <- diff(data$Share_in_land_area_Forest_Land, differences = 1)
rail_tracks_1 <- diff(data$Rail_tracks_KM , differences = 1)
motorways_len_1 <- diff(data$Length_of_motorways , differences = 1)
motorcycles_1 <- diff(data$Number_of_motorcycle , differences = 1)
aerial_freight_1 <- diff(data$Total_freight_loaded_and_unloaded , differences = 1)
```

```{r data for models}
bayes_1 <- cbind(greenhouse_1, harvested_rice_1, permanent_crops_1)
bayes_2 <- cbind(greenhouse_1, energy_imp_dep_1, oil_imports_1)
bayes_3 <- cbind(greenhouse_1, GDP_pc_1, fertilizer_1)
```

```{r remove clutter 1}
rm(list = ls()[!ls() %in% c("bayes_1", "bayes_2", "bayes_3")])
```

## Model 1

Model 1 includes: net greenhouse gas emission per capita, area of harvester rice, and share of land under permanent crops

```{r check data model 1}
bayes <- bayes_1
head(bayes)
bayes_ts <- as.ts(bayes)
plot(bayes_ts, main = "Model 1 time series", las = 1.5, lty = )
summary(bayes_ts)
```

## Model selection

```{r model selection model 1}
VARselect(bayes_ts, lag.max = 4,type = "const") 
bmodel <- gen_var(bayes_ts, p = 1, deterministic = "const")
y <- t(bmodel$data$Y)
x <- t(bmodel$data$Z)
```

# OLS estimation, Model 1

```{r OLS model 1}
beta_ols <- tcrossprod(y, x) %*% solve(tcrossprod(x)) # Calculate estimates
round(beta_ols, 3) # Round estimates and print
tab_ols_11 <- xtable(round(beta_ols, 3), caption = "OLS betas, Model 1", label = "tab:tab_ols_11")


e_ols <- y - beta_ols %*% x
e_sigma_ols <- tcrossprod(e_ols) / (ncol(y) - nrow(x))
round(e_sigma_ols, 2)
tab_ols_12 <- xtable(round(e_sigma_ols, 2), caption = "OLS var-covar, Model 1", label = "tab:tab_ols_12")
```

# Bayesian estimation, Model 1

```{r bayesian estimation model 1}

set.seed(1234567)
iter <- 20000 # Number of iterations of the Gibbs sampler
burnin <- 2000 # Number of burn-in draws
store <- iter - burnin

t <- ncol(y) # Number of observations
k <- nrow(y) # Number of endogenous variables
m <- k * nrow(x) # Number of estimated coefficients
```

```{r set priors model 1}
a_mu_prior <- matrix(c(beta_ols), m) # Vector of prior parameter means
a_v_i_prior <- diag(1, m) # Inverse of the prior covariance matrix

u_sigma_df_prior <- 2*k # Prior degrees of freedom
u_sigma_scale_prior <- diag(1, k) # Prior covariance matrix
u_sigma_df_post <- t + u_sigma_df_prior # Posterior degrees of freedom
```

```{r Initial Values model 1}
u_sigma_i <- solve(e_sigma_ols) #Inverse error variance-covariance

# Data containers for Gibss sampler
draws_a <- matrix(NA, m, store)
draws_sigma <- matrix(NA, k * k, store)
```

```{r Start Gibbs sampler model 1}
for (draw in 1:iter) {
  # Draw conditional mean parameters
  a <- post_normal(y, x, u_sigma_i, a_mu_prior, a_v_i_prior) #Draw the coefficients from a Normal density
  
  # Draw variance-covariance matrix
  u <- y - matrix(a, k) %*% x # Obtain residuals
  u_sigma_scale_post <- solve(u_sigma_scale_prior + tcrossprod(u))
  u_sigma_i <- matrix(rWishart(1, u_sigma_df_post, u_sigma_scale_post)[,, 1], k) #Draw from the iW density
  u_sigma <- solve(u_sigma_i) # Invert Sigma_i to obtain Sigma
  
  # Store draws
  if (draw > burnin) {
    draws_a[, draw - burnin] <- a
    draws_sigma[, draw - burnin] <- u_sigma
  }
}
```

```{r Gibss sampler results model 1}
A <- rowMeans(draws_a) # Obtain means for every row
A <- matrix(A, k) # Transform mean vector into a matrix
A <- round(A, 3) # Round values
dimnames(A) <- list(dimnames(y)[[1]], dimnames(x)[[1]]) # Rename matrix dimensions

A # Print
tab_bayes_A1 <- xtable(round(A, 3), caption = "Bayesian coefficients, Model 1", label = "tab:tab_bayes_A1")

Sigma <- rowMeans(draws_sigma) # Obtain means for every row
Sigma <- matrix(Sigma, k) # Transform mean vector into a matrix
Sigma <- round(Sigma, 2) # Round values
dimnames(Sigma) <- list(dimnames(y)[[1]], dimnames(y)[[1]]) # Rename matrix dimensions

Sigma # Print
tab_bayes_Sigma1 <- xtable(round(Sigma, 3), caption = "Bayesian var-covar, Model 1", label = "tab:tab_bayes_Sigma1")
```

```{r BVAR object model 1}
bvar_model <- bvar(y = bmodel$data$Y, x = bmodel$data$Z, A = draws_a[1:9,],
                 C = draws_a[10:12, ], Sigma = draws_sigma)
#bvar_model <- thin.bvar(bvar_model, thin = 2)
summary(bvar_model)

```

```{r Chain analysis model 1}
str(draws_a)
for (i in 1:nrow(draws_a)){
  par(mfrow = c(1, 2))
  ts.plot(draws_a[i,], 
          xlab = 'Number of iterations', 
          ylab = "Coefficient value", 
          main = paste0("Chain for coefficient ", i))
  acf(draws_a[i,], main = paste0("ACF for coefficient ", i))
}
plot(bvar_model)
```

```{r IRF Analysis model 1}
GIR_1 <- bvartools::irf(bvar_model, impulse = "harvested_rice_1", response = "greenhouse_1", n.ahead = 5, type = "gir")
round(GIR_1, 2)
tab_GIR_11 <- xtable(round(GIR_1, 3), caption = "GIRF betas, Model 1", label = "tab:tab_GIR_11")
plot(GIR_1, main = "GIRF, Impulse = harvested_rice, Response = greenhouse gas", xlab = "Periods ahead", ylab = "Response")

GIR_2 <- bvartools::irf(bvar_model, impulse = "permanent_crops_1", response = "greenhouse_1", n.ahead = 5, type = "gir")
round(GIR_2, 2)
tab_GIR_12 <- xtable(round(GIR_1, 3), caption = "GIRF betas, Model 1", label = "tab:tab_GIR_12")
plot(GIR_2, main = "GIRF, Impulse = permanent_crops, Response = greenhouse gas", xlab = "Periods ahead", ylab = "Response")
```

```{r Error Variance Decomposition model 1}
bvar_fevd_gir <- bvartools::fevd(bvar_model, response = "greenhouse_1", type = "gir")
round(bvar_fevd_gir, 2)
plot(bvar_fevd_gir, main = "GIR-based FEVD of Net Greenhouse gas emissions per capita")
```

```{r print LaTeX tables, Model 1}
print(tab_ols_11, caption.placement = "top") #OLS coefficients
cat("\n")
print(tab_ols_12, caption.placement = "top") #OLS error var-covar

cat("\n")

print(tab_bayes_A1, caption.placement = "top") #Bayesian coefficients
cat("\n")
print(tab_bayes_Sigma1, caption.placement = "top") #Bayesian error var-covar

cat("\n")

print(tab_GIR_11, caption.placement = "top") #GIRF 1 coefficients
cat("\n")
print(tab_GIR_12, caption.placement = "top") #GIRF 2 coefficients
```


```{r remove clutter 2}
rm(list = ls()[!ls() %in% c("bayes_1", "bayes_2", "bayes_3")])
```


## Model 2

Model 2 includes: net greenhouse gas emission per capita, energy import dependency, and oil imports

```{r check data model 2}
bayes <- bayes_2
head(bayes)
bayes_ts <- as.ts(bayes)
plot(bayes_ts, main = "Model 2 time series", las = 1.5)
summary(bayes_ts)
```

## Model selection

```{r model selection model 2}
VARselect(bayes_ts, lag.max = 4,type = "const") 
bmodel <- gen_var(bayes_ts, p = 1, deterministic = "const")
y <- t(bmodel$data$Y)
x <- t(bmodel$data$Z)
```

# OLS estimation, Model 2

```{r OLS model 2}
beta_ols <- tcrossprod(y, x) %*% solve(tcrossprod(x)) # Calculate estimates
round(beta_ols, 3) # Round estimates and print
tab_ols_21 <- xtable(round(beta_ols, 3), caption = "OLS betas, Model 2", label = "tab:tab_ols_11")


e_ols <- y - beta_ols %*% x
e_sigma_ols <- tcrossprod(e_ols) / (ncol(y) - nrow(x))
round(e_sigma_ols, 2)
tab_ols_22 <- xtable(round(e_sigma_ols, 2), caption = "OLS var-covar, Model 2", label = "tab:tab_ols_12")
```

# Bayesian estimation, Model 2

```{r bayesian estimation model 2}

set.seed(1234567)
iter <- 20000 # Number of iterations of the Gibbs sampler
burnin <- 2000 # Number of burn-in draws
store <- iter - burnin

t <- ncol(y) # Number of observations
k <- nrow(y) # Number of endogenous variables
m <- k * nrow(x) # Number of estimated coefficients
```

```{r set priors model 2}
a_mu_prior <- matrix(c(beta_ols), m) # Vector of prior parameter means
a_v_i_prior <- diag(1, m) # Inverse of the prior covariance matrix

u_sigma_df_prior <- 2*k # Prior degrees of freedom
u_sigma_scale_prior <- diag(1, k) # Prior covariance matrix
u_sigma_df_post <- t + u_sigma_df_prior # Posterior degrees of freedom
```

```{r Initial Values model 2}
u_sigma_i <- solve(e_sigma_ols)

# Data containers for Gibss sampler
draws_a <- matrix(NA, m, store)
draws_sigma <- matrix(NA, k * k, store)
```

```{r Start Gibbs sampler model 2}
for (draw in 1:iter) {
  # Draw conditional mean parameters
  a <- post_normal(y, x, u_sigma_i, a_mu_prior, a_v_i_prior) #Draw the coefficients from a Normal density
  
  # Draw variance-covariance matrix
  u <- y - matrix(a, k) %*% x # Obtain residuals
  u_sigma_scale_post <- solve(u_sigma_scale_prior + tcrossprod(u))
  u_sigma_i <- matrix(rWishart(1, u_sigma_df_post, u_sigma_scale_post)[,, 1], k) #Draw from the iW density
  u_sigma <- solve(u_sigma_i) # Invert Sigma_i to obtain Sigma
  
  # Store draws
  if (draw > burnin) {
    draws_a[, draw - burnin] <- a
    draws_sigma[, draw - burnin] <- u_sigma
  }
}
```

```{r Gibss sampler results model 2}
A <- rowMeans(draws_a) # Obtain means for every row
A <- matrix(A, k) # Transform mean vector into a matrix
A <- round(A, 3) # Round values
dimnames(A) <- list(dimnames(y)[[1]], dimnames(x)[[1]]) # Rename matrix dimensions

A # Print
tab_bayes_A2 <- xtable(round(A, 3), caption = "Bayesian coefficients, Model 2", label = "tab:tab_bayes_A2")

Sigma <- rowMeans(draws_sigma) # Obtain means for every row
Sigma <- matrix(Sigma, k) # Transform mean vector into a matrix
Sigma <- round(Sigma, 2) # Round values
dimnames(Sigma) <- list(dimnames(y)[[1]], dimnames(y)[[1]]) # Rename matrix dimensions

Sigma # Print
tab_bayes_Sigma2 <- xtable(round(Sigma, 3), caption = "Bayesian var-covar, Model 2", label = "tab:tab_bayes_Sigma2")
```

```{r BVAR object model 2}
bvar_model <- bvar(y = bmodel$data$Y, x = bmodel$data$Z, A = draws_a[1:9,],
                 C = draws_a[10:12, ], Sigma = draws_sigma)
#bvar_model <- thin.bvar(bvar_model, thin = 2)
summary(bvar_model)

```

```{r Chain analysis model 2}
str(draws_a)
for (i in 1:nrow(draws_a)){
  par(mfrow = c(1, 2))
  ts.plot(draws_a[i,], 
          xlab = 'Number of iterations', 
          ylab = "Coefficient value", 
          main = paste0("Chain for coefficient ", i))
  acf(draws_a[i,], main = paste0("ACF for coefficient ", i))
}
plot(bvar_model)
```

```{r IRF Analysis model 2}
GIR_1 <- bvartools::irf(bvar_model, impulse = "energy_imp_dep_1", response = "greenhouse_1", n.ahead = 5, type = "gir")
round(GIR_1, 2)
tab_GIR_21 <- xtable(round(GIR_1, 3), caption = "GIRF betas, Model 2", label = "tab:tab_GIR_21")
plot(GIR_1, main = "GIRF, Impulse = harvested_rice, Response = greenhouse gas", xlab = "Periods ahead", ylab = "Response")

GIR_2 <- bvartools::irf(bvar_model, impulse = "oil_imports_1", response = "greenhouse_1", n.ahead = 5, type = "gir")
round(GIR_2, 2)
tab_GIR_22 <- xtable(round(GIR_1, 3), caption = "GIRF betas, Model 2", label = "tab:tab_GIR_22")
plot(GIR_2, main = "GIRF, Impulse = permanent_crops, Response = greenhouse gas", xlab = "Periods ahead", ylab = "Response")
```

```{r Error Variance Decomposition model 2}
bvar_fevd_gir <- bvartools::fevd(bvar_model, response = "greenhouse_1", type = "gir")
round(bvar_fevd_gir, 2)
plot(bvar_fevd_gir, main = "GIR-based FEVD of Net Greenhouse gas emissions per capita")
```


```{r print LaTeX tables, Model 2}
print(tab_ols_21, caption.placement = "top") #OLS coefficients
cat("\n")
print(tab_ols_22, caption.placement = "top") #OLS error var-covar

cat("\n")

print(tab_bayes_A2, caption.placement = "top") #Bayesian coefficients
cat("\n")
print(tab_bayes_Sigma2, caption.placement = "top") #Bayesian error var-covar

cat("\n")

print(tab_GIR_21, caption.placement = "top") #GIRF 1 coefficients
cat("\n")
print(tab_GIR_22, caption.placement = "top") #GIRF 2 coefficients
```


```{r remove clutter 3}
rm(list = ls()[!ls() %in% c("bayes_1", "bayes_2", "bayes_3")])
```


## Model 3

Model 3 includes: net greenhouse gas emission per capita, GDP per capita, and fertilizer per ha

```{r check data model 3}
bayes <- bayes_3
head(bayes)
bayes_ts <- as.ts(bayes)
plot(bayes_ts, main = "Model 3 time series", las = 1.5)
summary(bayes_ts)
```

## Model selection

```{r model selection model 3}
VARselect(bayes_ts, lag.max = 4,type = "const") 
bmodel <- gen_var(bayes_ts, p = 1, deterministic = "const")
y <- t(bmodel$data$Y)
x <- t(bmodel$data$Z)
```

# OLS estimation, Model 3

```{r OLS model 3}
beta_ols <- tcrossprod(y, x) %*% solve(tcrossprod(x)) # Calculate estimates
round(beta_ols, 3) # Round estimates and print
tab_ols_31 <- xtable(round(beta_ols, 3), caption = "OLS betas, Model 3", label = "tab:tab_ols_31")


e_ols <- y - beta_ols %*% x
e_sigma_ols <- tcrossprod(e_ols) / (ncol(y) - nrow(x))
round(e_sigma_ols, 2)
tab_ols_32 <- xtable(round(e_sigma_ols, 2), caption = "OLS var-covar, Model 3", label = "tab:tab_ols_32")
```

# Bayesian estimation, Model 3

```{r bayesian estimation model 3}

set.seed(1234567)
iter <- 20000 # Number of iterations of the Gibbs sampler
burnin <- 2000 # Number of burn-in draws
store <- iter - burnin

t <- ncol(y) # Number of observations
k <- nrow(y) # Number of endogenous variables
m <- k * nrow(x) # Number of estimated coefficients
```

```{r set priors model 3}
a_mu_prior <- matrix(0, m) # Vector of prior parameter means
a_v_i_prior <- diag(1, m) # Inverse of the prior covariance matrix

u_sigma_df_prior <- 2*k # Prior degrees of freedom
u_sigma_scale_prior <- diag(1, k) # Prior covariance matrix
u_sigma_df_post <- t + u_sigma_df_prior # Posterior degrees of freedom
```

```{r Initial Values model 3}
u_sigma_i <- solve(e_sigma_ols)

# Data containers for Gibss sampler
draws_a <- matrix(NA, m, store)
draws_sigma <- matrix(NA, k * k, store)
```

```{r Start Gibbs sampler model 3}
for (draw in 1:iter) {
  # Draw conditional mean parameters
  a <- post_normal(y, x, u_sigma_i, a_mu_prior, a_v_i_prior) #Draw the coefficients from a Normal density
  
  # Draw variance-covariance matrix
  u <- y - matrix(a, k) %*% x # Obtain residuals
  u_sigma_scale_post <- solve(u_sigma_scale_prior + tcrossprod(u))
  u_sigma_i <- matrix(rWishart(1, u_sigma_df_post, u_sigma_scale_post)[,, 1], k) #Draw from the iW density
  u_sigma <- solve(u_sigma_i) # Invert Sigma_i to obtain Sigma
  
  # Store draws
  if (draw > burnin) {
    draws_a[, draw - burnin] <- a
    draws_sigma[, draw - burnin] <- u_sigma
  }
}
```

```{r Gibss sampler results model 3}
A <- rowMeans(draws_a) # Obtain means for every row
A <- matrix(A, k) # Transform mean vector into a matrix
A <- round(A, 3) # Round values
dimnames(A) <- list(dimnames(y)[[1]], dimnames(x)[[1]]) # Rename matrix dimensions

A # Print
tab_bayes_A3 <- xtable(round(A, 3), caption = "Bayesian coefficients, Model 3", label = "tab:tab_bayes_A3")

Sigma <- rowMeans(draws_sigma) # Obtain means for every row
Sigma <- matrix(Sigma, k) # Transform mean vector into a matrix
Sigma <- round(Sigma, 2) # Round values
dimnames(Sigma) <- list(dimnames(y)[[1]], dimnames(y)[[1]]) # Rename matrix dimensions

Sigma # Print
tab_bayes_Sigma3 <- xtable(round(Sigma, 3), caption = "Bayesian var-covar, Model 3", label = "tab:tab_bayes_Sigma3")
```

```{r BVAR object model 3}
bvar_model <- bvar(y = bmodel$data$Y, x = bmodel$data$Z, A = draws_a[1:9,],
                 C = draws_a[10:12, ], Sigma = draws_sigma)
#bvar_model <- thin.bvar(bvar_model, thin = 2)
summary(bvar_model)

```

```{r Chain analysis}
str(draws_a)
for (i in 1:nrow(draws_a)){
  par(mfrow = c(1, 2))
  ts.plot(draws_a[i,], 
          xlab = 'Number of iterations', 
          ylab = "Coefficient value", 
          main = paste0("Chain for coefficient ", i))
  acf(draws_a[i,], main = paste0("ACF for coefficient ", i))
}
plot(bvar_model)
```

```{r IRF Analysis model 3}
GIR_1 <- bvartools::irf(bvar_model, impulse = "GDP_pc_1", response = "greenhouse_1", n.ahead = 5, type = "gir")
round(GIR_1, 2)
tab_GIR_31 <- xtable(round(GIR_1, 3), caption = "GIRF betas, Model 3", label = "tab:tab_GIR_31")
plot(GIR_1, main = "GIRF, Impulse = harvested_rice, Response = greenhouse gas", xlab = "Periods ahead", ylab = "Response")

GIR_2 <- bvartools::irf(bvar_model, impulse = "fertilizer_1", response = "greenhouse_1", n.ahead = 5, type = "gir")
round(GIR_2, 2)
tab_GIR_32 <- xtable(round(GIR_1, 3), caption = "GIRF betas, Model 3", label = "tab:tab_GIR_32")
plot(GIR_2, main = "GIRF, Impulse = permanent_crops, Response = greenhouse gas", xlab = "Periods ahead", ylab = "Response")
```

```{r Error Variance Decomposition model 3}
bvar_fevd_gir <- bvartools::fevd(bvar_model, response = "greenhouse_1", type = "gir")
round(bvar_fevd_gir, 2)
plot(bvar_fevd_gir, main = "GIR-based FEVD of Net Greenhouse gas emissions per capita")
```
```{r print LaTeX tables, Model 3}
print(tab_ols_31, caption.placement = "top") #OLS coefficients
cat("\n")
print(tab_ols_32, caption.placement = "top") #OLS error var-covar

cat("\n")

print(tab_bayes_A3, caption.placement = "top") #Bayesian coefficients
cat("\n")
print(tab_bayes_Sigma3, caption.placement = "top") #Bayesian error var-covar

cat("\n")

print(tab_GIR_31, caption.placement = "top") #GIRF 1 coefficients
cat("\n")
print(tab_GIR_32, caption.placement = "top") #GIRF 2 coefficients
```